The transition redshift as a probe of reionization

### 2019-08-15 paper/ms.tex
Small text edits

% Abstract of the paper
\begin{abstract}
The early stages of the Epoch of Reionization (EoR), probed by the 21~cm line,
are sensitive to the detailed formation of the first galaxies. An important
transition occurs on large scales at $\avg{x_i}\sim0.15$, when the 21~cm field
transitions from being positively correlated with the galaxy field to being
negatively correlated. The redshift at which this transition occurs (the
``transition redshift'') is, in principle, sensitive to both the structure of
the 21~cm field but also the galaxy field. However, by considering a fixed
model for the EoR and varying the parameters of a simple model for the galaxy
field in a mock [O~\textsc{iii}]-emitter sample cross-correlation, we show
that the transition redshift is in fact insensitive to the structure of the
selected galaxy sample. We show that prospects for measuring the transition
redshift are feasible in the near-term with a combination of LOFAR and JWST.
Being derived from a cross-correlation, the transition redshift is less
impacted by foreground contamination currently inhibiting 21~cm auto-spectrum
measurements. Therefore, the transition redshift is an interesting probe of
the early stages of the EoR, and its detectability and interpretability
deserve further study.
\end{abstract}

>>>>

% Abstract of the paper
\begin{abstract}
The early stages of the Epoch of Reionization (EoR), probed by the 21~cm line,
are sensitive to the detailed formation of the first galaxies. An important
transition occurs on large scales at $z\sim10$, when the 21~cm field
transitions from being positively correlated with the density field to being
negatively correlated. The redshift at which this transition occurs (the
``transition redshift'') is in principle measurable if the 21~cm field can be
cross-correlated with a tracer of the density field (such as galaxies or a
line intensity map) at that high redshift. Since the transition redshift is
derived from a cross-correlation, it is in principle sensitive to the
structure of both the 21~cm field and the tracer used to measure it. However,
by considering a fixed model for the EoR and varying the parameters of a
simple model for a H$\alpha$ intensity map cross-correlation, we show that the
transition redshift is in fact very insensitive to the structure of the
density tracer. A simple analytic argument motivates this result. We show that
prospects for measuring the transition redshift are feasible in the near-term
with a combination of LOFAR and JWST. Being derived from a cross-correlation,
the transition redshift is less impacted by foreground contamination currently
inhibiting 21~cm auto-spectrum measurements. Therefore, the transition
redshift is an interesting probe of the early stages of the EoR, and its
detectability and interpretability deserve further study.
\end{abstract}
